\textbf{EECS 340: Assignment 1}

### 2020-01-28 assignment_1/article.tex
💄 Fix some expressions in Problem 2 for better reading continuity.

% \newpage

@@

The following is graphical demenstration of \textit{TwoSum(A, B, 5, 12)}:
\tikzset{
mymat/.style={
  matrix of math nodes,
  text height=2.5ex,
  text depth=0.75ex,
  text width=3.25ex,
  align=center,
  column sep=-\pgflinewidth
  },
mymats/.style={
  mymat,
  nodes={draw,fill=#1}
  }
}

@@

Assume we get $A[i] + B[j] = k$ within an iteration of the \inlinecode{while} loop, we either have $k < x$ or $k > x$. In both cases, we may confidently say that there will be no $a + b = k$. As the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$. Thus, if there is any $a + b = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop. Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a, b)$ combination where $a + b = x$. By this, the loop invariant is held true for all cases within the \inlinecode{while} loop.\newline

@@

As there is no $(a, b)$ combination available to form a $x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the next interation. Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified.

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $O(n)$.

>>>>

\newpage

@@

The following is graphical demenstration of \inlinecode{TwoSum(A, B, 5, 12)}:
\tikzset{
mymat/.style={
  matrix of math nodes,
  text height=2.5ex,
  text depth=0.75ex,
  text width=3.25ex,
  align=center,
  column sep=-\pgflinewidth
  },
mymats/.style={
  mymat,
  nodes={draw,fill=#1}
  }
}

@@

Assume we get $A[i] + B[j] = k$ within an iteration of the \inlinecode{while} loop, we either have $k < x$ or $k > x$. In both cases, we may confidently say that there will be no $a + b = k$; as the index of $a$ must be smaller than $i$ and the index of $b$ must be greater than $j$. Thus, if there is any $a + b = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop. Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a, b)$ combination where $a + b = x$. By this, the loop invariant is held true for all cases within the \inlinecode{while} loop.\newline

@@

As there is no $(a, b)$ combination available to form $a+b = x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$. Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $\Theta(n)$.
